An Airdrop That Preserves Recipient Privacy

### 2019-01-12 paper/paper.tex
edits

Next we argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly. 
Write $\hat{\rv}$ generated on line~\eqref{ln:randv} in the simulation
as $\hat{\rv} = \big(r_\text{w}, r_\text{w2}, r_\text{s1}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}, r_\text{s2} \big)$.
Then the simulated $\Zv_q$ is computed as:
\begin{equation} \label{eq:sim}
\Zv_q \deq \left(\begin{array}{l}
Z_1 \gets \hat{c}_1^\mathit{ch} \cdot g^{\lfloor r_\text{w}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1}/\ell \rfloor} ,\quad
Z_2 \gets \hat{c}_2^\mathit{ch} \cdot g^{\lfloor r_\text{a}/\ell \rfloor} \cdot h^{\lfloor r_\text{s2}/\ell \rfloor} , \AlgSep
Z_3 \gets g^{\lfloor r_\text{w2}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1w}/\ell \rfloor} / \hat{c}_1^{\lfloor r_\text{w}/\ell \rfloor},\quad
Z_4 \gets g^{\lfloor r_\text{na}/\ell \rfloor} \cdot h^{\lfloor r_\text{sa}/\ell \rfloor} / \hat{c}^{\lfloor r_\text{a}/\ell \rfloor}, \AlgSep
Z_5 \gets \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2}/\ell \rfloor - \lfloor r_\text{na}/\ell \rfloor 
\end{array}\right) \in \GG^4 \times \ZZ.  
\end{equation}
Let's start with $Z_5 \in \ZZ$.  
In a real transcript 
$Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
          \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
Therefore, because $\mathit{w2} - \mathit{na} = t$, we have
that $Z_5$ in a real transcript satifies
\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
where $\Delta \in \{0, \pm 1\}$. 
In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
and $\lfloor r_\text{na} / \ell \rfloor$ 
are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
as in the the simulated $Z_5$ in~\eqref{eq:sim}.
The only difference is that the real distribution is shifted by $\Delta$
where as the simulated distribution is not.  
However this $\Delta$ only negligibly affects the statistical distance
between the real and simulated distributions. 
The reason is that in both distributions 
every possible value in the range of $Z_5$, 
except possibly at the edges, 
is obtained from exactly $\ell^2$ values of $(r_\text{w2}, r_\text{na})$. 
We thus conclude that the simulated $Z_5$ in~\eqref{eq:sim} 
is statistically close to its real distribution.

Essentially the same argument shows that $Z_1, Z_2, Z_3, Z_4$ are
also simulated correctly. 
For example, in a real transcript 
\begin{align*}
    Z_1 & \deq g^{\lfloor (\mathit{ch}\cdot w + r_\text{w}) / \ell \rfloor} \cdot 
             h^{\lfloor (\mathit{ch}\cdot \mathit{s1} + r_\text{s1}) / \ell \rfloor} = \\
       & =   g^{\lfloor (\mathit{ch}\cdot w) / \ell \rfloor} \cdot
             h^{\lfloor (\mathit{ch}\cdot s1) / \ell \rfloor} \cdot
             g^{\lfloor r_\text{w} / \ell \rfloor + \Delta_\text{w}} \cdot 
             h^{\lfloor r_\text{s1} / \ell \rfloor + \Delta_\text{s1}} =  \\
       & = (\tilde{c}_1)^\mathit{ch} \cdot
             g^{\lfloor r_\text{w} / \ell \rfloor} \cdot 
             h^{\lfloor r_\text{s1} / \ell \rfloor} \cdot 
             \left[ (g^{1/\ell})^{\delta_\text{w} + \ell \cdot \Delta_\text{w}} \cdot 
               (h^{1/\ell})^{\delta_\text{s1} + \ell \cdot \Delta_\text{s1}} \right]
\end{align*}
where $\Delta_\text{w}, \Delta_\text{s1} \in \{0,1\}$ as for $Z_5$, 
and $\delta_\text{w} \deq (\mathit{ch} \cdot w \bmod \ell) \in \range{\ell}$
and $\delta_\text{s1} \deq (\mathit{ch} \cdot \mathit{s1} \bmod \ell) \in \range{\ell}$.
Hence, $Z_1$ in a real transcript is distributed as 
the simulated $Z_1$ in~\eqref{eq:sim}, where the only
difference is the quantity 
$\Delta \deq (g^{1/\ell})^{\delta_\text{w} - \ell \cdot \Delta_\text{w}} \cdot 
               (h^{1/\ell})^{\delta_\text{s1} - \ell \cdot \Delta_\text{s1}} \in \GG$. 
We claim that this $\Delta$ only negligibly affects the statistical distance
between the real and simulated distributions. 
{\bf TODO:} explain why.

>>>>

Next we argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly. 
Write $\hat{\rv}$ generated on line~\eqref{ln:randv} in the simulation
as $\hat{\rv} = \big(r_\text{w}, r_\text{w2}, r_\text{s1}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}, r_\text{s2} \big)$.
Then the simulated $\Zv_q$ is computed as:
\begin{equation} \label{eq:sim}
\Zv_q \deq \left(\begin{array}{l}
Z_1 \gets \hat{c}_1^\mathit{ch} \cdot g^{\lfloor r_\text{w}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1}/\ell \rfloor} ,\quad
Z_2 \gets \hat{c}_2^\mathit{ch} \cdot g^{\lfloor r_\text{a}/\ell \rfloor} \cdot h^{\lfloor r_\text{s2}/\ell \rfloor} , \AlgSep
Z_3 \gets g^{\lfloor r_\text{w2}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1w}/\ell \rfloor} / \hat{c}_1^{\lfloor r_\text{w}/\ell \rfloor},\quad
Z_4 \gets g^{\lfloor r_\text{na}/\ell \rfloor} \cdot h^{\lfloor r_\text{sa}/\ell \rfloor} / \hat{c}^{\lfloor r_\text{a}/\ell \rfloor}, \AlgSep
Z_5 \gets \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2}/\ell \rfloor - \lfloor r_\text{na}/\ell \rfloor 
\end{array}\right) \in \GG^4 \times \ZZ.  
\end{equation}
Let's start with $Z_5 \in \ZZ$.  
In a real transcript 
$Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
          \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
Therefore, because $\mathit{w2} - \mathit{na} = t$, we have
that $Z_5$ in a real transcript satifies
\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
where $\Delta \in \{0, \pm 1\}$. 
In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
and $\lfloor r_\text{na} / \ell \rfloor$ 
are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
as in the the simulated $Z_5$ in~\eqref{eq:sim}.
The only difference is that the real distribution is shifted by $\Delta$
where as the simulated distribution is not.  
However this $\Delta$ only negligibly affects the statistical distance
between the real and simulated distributions. 
The reason is that in both distributions, 
every possible value in the range of $Z_5$, 
except possibly at the edges, 
is obtained from the same number of values 
for the pair $(r_\text{w2}, r_\text{na})$. 
%%  would be good to prove this as a general lemma.
We thus conclude that the simulated $Z_5$ in~\eqref{eq:sim} 
is statistically close to its real distribution.

Essentially the same argument shows that $Z_1, Z_2, Z_3, Z_4$ are
also simulated correctly. 
For example, in a real transcript, where $c_1 = g^w h^\mathit{s1}$, we have
\begin{align*}
    Z_1 & \deq g^{\lfloor (\mathit{ch}\cdot w + r_\text{w}) / \ell \rfloor} \cdot 
             h^{\lfloor (\mathit{ch}\cdot \mathit{s1} + r_\text{s1}) / \ell \rfloor} = \\
       & =   g^{\lfloor (\mathit{ch}\cdot w) / \ell \rfloor} \cdot
             h^{\lfloor (\mathit{ch}\cdot s1) / \ell \rfloor} \cdot
             g^{\lfloor r_\text{w} / \ell \rfloor + \Delta_\text{w}} \cdot 
             h^{\lfloor r_\text{s1} / \ell \rfloor + \Delta_\text{s1}} =  \\
       & = (c_1^{1/\ell})^\mathit{ch} \cdot
             g^{\lfloor r_\text{w} / \ell \rfloor} \cdot 
             h^{\lfloor r_\text{s1} / \ell \rfloor} \cdot 
             \left[ (g^{1/\ell})^{\delta_\text{w} + \ell \cdot \Delta_\text{w}} \cdot 
               (h^{1/\ell})^{\delta_\text{s1} + \ell \cdot \Delta_\text{s1}} \right]
\end{align*}
where $\Delta_\text{w}, \Delta_\text{s1} \in \{0,1\}$,
and $\delta_\text{w} \deq (\mathit{ch} \cdot w \bmod \ell) \in \range{\ell}$
and $\delta_\text{s1} \deq (\mathit{ch} \cdot \mathit{s1} \bmod \ell) \in \range{\ell}$.
Hence, $Z_1$ in a real transcript is distributed as 
the simulated $Z_1$ in~\eqref{eq:sim}, where the only
difference is the quantity 
$\Delta \deq (g^{1/\ell})^{\delta_\text{w} - \ell \cdot \Delta_\text{w}} \cdot 
               (h^{1/\ell})^{\delta_\text{s1} - \ell \cdot \Delta_\text{s1}} \in \GG$. 
We claim that this $\Delta$ only negligibly affects the statistical distance
between the real and simulated distributions. 
{\bf TODO:} explain why.
